Wykorzystanie Ethereum do budowy zdecentralizowanej aplikacji

### 2018-04-05 article.tex
Translate keywords
Add reference to webpage

% Display polish characters
\usepackage{polski}
\usepackage[utf8]{inputenc}

@@

\title{Wykorzystanie Blockchainu Ethereum do budowy zdecentralizowanej aplikacji}
\author{Wojciech Korzeniowski}
\institute{
  Instytut Informatyki\\Wydział Elektroniki i Technik Informacyjnych\\Politechnika Warszawska\\
  \url{http://www.ii.pw.edu.pl/}
}

@@

  Opis zdecentralizowanej aplikacji zbudowanej z wykorzystaniem smartkontraktów
  Ethereum.
  \keywords{Smart contract \and Blockchain \and DApp}

@@

\begin{theorem}
  This is a sample theorem. The run-in heading is set in bold, while
  the following text appears in italics. Definitions, lemmas,
  propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
  Proofs, examples, and remarks have the initial word in italics,
  while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
  \bibitem{ref_article1}
  Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

  \bibitem{ref_lncs1}
  Author, F., Author, S.: Title of a proceedings paper. In: Editor,
  F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
  Springer, Heidelberg (2016). \doi{10.10007/1234567890}

  \bibitem{ref_book1}
  Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
  Location (1999)

  \bibitem{ref_proc1}
  Author, A.-B.: Contribution title. In: 9th International Proceedings
  on Proceedings, pp. 1--2. Publisher, Location (2010)

  \bibitem{ref_url1}
  LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
  Oct 2017
\end{thebibliography}
\end{document}

>>>>

% Display polish characters
\usepackage[polish]{babel}
\usepackage[utf8]{inputenc}

\renewcommand{\keywords}[1]{
    \def\and{* }
    \begingroup
    \par
    \bigskip
    \noindent\textbf{Słowa Kluczowe: } #1\par
    \endgroup
}

@@

\title{Wykorzystanie Ethereum do budowy zdecentralizowanej aplikacji}
\author{Wojciech Korzeniowski}
\institute{
  Instytut Informatyki\\Wydział Elektroniki i Technik Informacyjnych\\Politechnika Warszawska\\
  \url{http://www.ii.pw.edu.pl/}
}

@@

  Opis zdecentralizowanej aplikacji zbudowanej zbudowanej na platformie Ethereum
  z wykorzystaniem smartkontraktów Ethereum\cite{ethereum}.
  \keywords{Smart contract \and Blockchain \and DApp}

@@

\begin{theorem}
  This is a sample theorem. The run-in heading is set in bold, while
  the following text appears in italics. Definitions, lemmas,
  propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
  Proofs, examples, and remarks have the initial word in italics,
  while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
  \bibitem{ethereum} Ethereum Homepage, \url{https://www.ethereum.org/}
\end{thebibliography}
\end{document}
